---
title: "Learning Note of International Trade"
output: html_document
runtime: shiny
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

I would use this notebook as my learning note of "International Trade" book. I will try my best to mark the source where I quote information from, no matter it is from a book or something else. And please feel free to let me know if there is anything that you think is inproper, I will review it and adjust it if it is neccessary.

## 1. Gravity model

Let me type in formula first



$T_{ij} = A \times Y_{i} \times Y_{j} / D_{ij}$  <br>
In which $A$ is a constant term, $Y_{i}$ and $Y_{j}$ is GDP of the corresponding country, $T_{ij}$ is trade volume between countries, and $D_{ij}$ represents distant between countries.<br>

Then let's type/select parameters to verify if the formula holds
*GDP data is from 2017, unit is million in USD*

```{r eruptions, echo=FALSE}
inputPanel(
  selectInput("country_1", label = "Country i",
              choices = c('USA'), selected = 'USA'),
  selectInput("country_2", label = "Country j",
              choices = c('UK'), selected = 'UK'),
  numericInput("A", label = "Constant A",
              value=0.001)
)

renderText({
  paste('Given the formula, the simulated trade value between ',input$country_1,'and',input$country_2,' is ',round(input$A*19485394*2637866/6000,2),' Million USD  ')
})

```

To be developed


